A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-08-30 ionic_liquids.tex
Changes in author affiliations

%% Group authors per affiliation:
\author[rvt]{A.J.~Silveira}
\author[rvt]{S.~Pereda}
\author[focal,els]{F.W.~Tavares}
\author[focal]{C.R.A.~Abreu\corref{cor1}}
\ead{abreu@eq.ufrj.br}

\address[rvt]{Planta Piloto de Ingenier\'ia Qu\'imica, PLAPIQUI, Universidad Nacional del Sur,Camino La Carrindanga Km 7-CC: 717, Bah\'ia Blanca, Argentina}
\address[focal]{Chemical Engineering Department, Escola de Qu\'imica, Universidade Federal do Rio de Janeiro,Rio de Janeiro, RJ 21941-909, Brazil}
\address[els]{COPPE, Universidade Federal do Rio de Janeiro, Rio de Janeiro, RJ 21941-909, Brazil}

>>>>

%% Group authors per affiliation:
\author[plapiqui,msk]{A.J.~Silveira}
\author[plapiqui]{S.~Pereda}
\author[eq-ufrj,coppe-ufrj]{F.W.~Tavares}
\author[eq-ufrj]{C.R.A.~Abreu\corref{cor1}}
\ead{abreu@eq.ufrj.br}

\address[plapiqui]{Planta Piloto de Ingenier\'ia Qu\'imica (PLAPIQUI), Universidad Nacional del Sur, Bah\'ia Blanca, Argentina}
\address[msk]{Computational \& Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York, NY, USA}
\address[eq-ufrj]{Chemical Engineering Department, Escola de Qu\'imica, Universidade Federal do Rio de Janeiro, Rio de Janeiro, Brazil}
\address[coppe-ufrj]{Chemical Engineering Program, Alberto Luiz Coimbra Institute for Graduate Studies and Research in Engineering (COPPE), Universidade Federal do Rio de Janeiro, Rio de Janeiro, Brazil}
